### 2019-06-04 2-Chapters/3-Chapter/chapter3.tex
Typos
Done for now
Lots of small change haha

\TODOL{Intégrer les commentaires de Christophe, le plus rapidement possible !}

@@

\paragraph{Publications.}
%
This chapter is based on the following publication: \cite{SMPyBanditsJMLR}.
The code for SMPyBandits is hosted online at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}} or \texttt{\href{https://SMPyBandits.RTFD.io/}{SMPyBandits.RTFD.io}}, and all the library is freely publicly released under the MIT open-source License.

>>>>

\TODOL{Abstract ici et plus court, et petite introduction !}
\TODOL{Analyser les expériences les plus récentes et décrire mieux en 3.2, et refaire toutes les courbes pour 3.2 et 3.3}

@@

\paragraph{Publications.}
%
This chapter is based on our article \cite{SMPyBanditsJMLR}.
The code for SMPyBandits is hosted online at \texttt{\href{https://GitHub.com/SMPyBandits/SMPyBandits/}{GitHub.com/SMPyBandits/SMPyBandits}}, its documentation is at \texttt{\href{https://SMPyBandits.GitHub.io/}{SMPyBandits.GitHub.io}} or \texttt{\href{https://SMPyBandits.RTFD.io/}{SMPyBandits.RTFD.io}}, and all the library is freely publicly released under the MIT open-source License.

### 2019-06-04 2-Chapters/4-Chapter/chapter4.tex
Typos
Lots of small change haha

\TODOL{Intégrer les commentaires de Christophe, le plus rapidement possible !}

@@

This chapter is mainly based on the following publications: \cite{Bonnefoi17,Besson2018ICT,Besson2019WCNC,Bonnefoi2019WCNC}.

>>>>

\TODOL{Abstract ici et plus court, et petite introduction !}

@@

This chapter is mainly based on our articles \cite{Bonnefoi17,Besson2018ICT,Besson2019WCNC,Bonnefoi2019WCNC}.

### 2019-06-04 2-Chapters/5-Chapter/chapter5.tex
On the one hand… on the other hand
- NOT on one hand
- NOT on the first hand
Lots of small change haha

This chapter is mainly based on the following publication: \cite{Besson2018ALT}.

@@

On the first hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in[M]$ knows its ID $j$ (we criticize this unrealistic assumption in Section~\ref{par:5:knowingYourIDinMPBanditsGame} above).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our algorithm \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches the conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in[M]$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.

>>>>

This chapter is mainly based on our article \cite{Besson2018ALT}.

@@

On the one hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in[M]$ knows its ID $j$ (we criticize this unrealistic assumption in Section~\ref{par:5:knowingYourIDinMPBanditsGame} above).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our algorithm \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches the conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in[M]$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.

### 2019-06-04 2-Chapters/6-Chapter/chapter6.tex
My thesis is so long, and so stupid
Thanks Christophe for comments on Ch2
SHIT I'm going home
Typos
Lots of small change haha

% \chapter{Non-Stationary MAB Models and Possible Applications for IoT Networks}
\chapter{The Piece-wise Stationary MAB Model and the GLR-klUCB Algorithm}
\label{chapter:6}
\minitoc

@@

\paragraph{Publications.}
%
This chapter is based on the following publications: \cite{Besson2019GLRT,Besson2019Gretsi}.

>>>>

% \chapter{Non-Stationary MAB Models and Possible Applications for IoT Networks}
% \chapter{The Piece-wise Stationary MAB Model and the GLR-klUCB Algorithm}
\chapter{Piece-Wise Stationary Multi-Armed Bandits}
\label{chapter:6}
\minitoc

\TODOL{Abstract ici et plus court, et petite introduction !}

@@

\paragraph{Publications.}
%
This chapter is based on our articles \cite{Besson2019GLRT,Besson2019Gretsi}.
